---
output:
  pdf_document: default
  html_document: default
---
Homework 2 - [Team 09]
========================================================

### Task 0 - Load the data

```{r message = FALSE}
#install.packages("repurrrsive")
library(dplyr)
library(purrr)
library(tibble)
#library(repurrrsive)
library(stringr)
library(knitr)

load("lego_sales.RData")
```


### Task 1 - Tidying the data

Write up: \
1. We first create a dataframe[D] that contains all customers' information (excluding purchases-related ones). \
2. Our objective is to create a dataframe where each row corresponds to a particular transaction. Therefore, we determine the number of purchases[NUM_PURCHASES] made by each customer. We then create a matrix[FINAL] that replicates each row of [D] according to the number of purchases made by each customer.\
3. We then proceed with adding the data for each purchase. We create a matrix[HALF2] with the total number of purchases [NUM_PURCHASES] as the number of rows, and the maximal number of data entries contained in each transaction as the number of columns. We note that each transaction contains 10 entries for all customers, yet we include this step to make the code more robust. We then loop through each customer's purchases to extract information and put that information into each row of [HALF2].\
4. We combine [FINAL] and [HALF2], and get the clean dataset. We also coerce certain variable types to facilitate the analysis in part 2.\

```{r}
list_cols = map(sales, ~ map_int(., length) )  %>% 
     map(~ which(. > 1)) %>% 
     unlist() %>% 
     names() %>% 
     unique()
d = map_df(
     sales, 
     function(row)
     {
         map_at(row, list_cols, list)
     }
 )

d$purchases = NULL
num_purchases = map(sales, "purchases") %>% map_int(length)
final = d %>%slice(rep(1:n(), num_purchases))

cols = map(sales, "purchases") %>% map(~map_int(.,length)) %>% unlist() %>% max()
half2 = matrix(data = NA, nrow = sum(num_purchases), ncol = cols)

iii = 0

for (i in 1:length(sales)){
  for (j in 1:num_purchases[i]){
    half2[iii+j,] = map(sales[i],"purchases")[[1]][[j]] %>% unlist()
  }
  iii = iii + num_purchases[i]
}

colnames(half2) = map(sales[1], "purchases")[[1]][[1]] %>% names()

kkk = cbind(final, half2)
lego_sales = as_tibble(kkk) 

lego_sales$Quantity = as.integer(lego_sales$Quantity)
lego_sales$Pieces = as.numeric(as.character(lego_sales$Pieces))
lego_sales$USPrice = as.numeric(as.character(lego_sales$USPrice))

lego_sales
```


<br/>

## Task 2 - Processing the data


1. What was the most common first name of purchasers? Last name?

```{r}
#first name
lego_sales %>% 
  
  select(first_name:last_name) %>%
  unique() %>%
  group_by(first_name) %>%
  summarize(number = n()) %>%
  filter(number == max(number)) %>%
  kable()

#last name
lego_sales %>% 
  
  select(first_name:last_name) %>%
  unique() %>%
  group_by(last_name) %>%
  summarize(number = n()) %>%
  filter(number == max(number)) %>%
  kable()

```

The most common first names are Jacob and Michael, and the most common last names are Brown, Scott, Smith and Williams. We first pick names(first name/last name) from the data frame, make every name unique, and pick the first name/last name that appear the most times.

<br/>

2. What are the five most popular lego sets based on these data?

```{r}
lego_sales %>%
  
  select(Name,Quantity) %>%
  group_by(Name) %>%
  summarize(total = sum(Quantity)) %>%
  arrange(desc(total)) %>%
  filter(total >= total[5]) %>% 
  kable()

```

From the table above we can see the five most popular sets. We pick names of sets and quatities of sold sets from the data frame, and compare the total quantities of sold sets by set names.

<br/>

3. Which five customers have spent the most money so far and how much have they spent?

```{r}
lego_sales %>% 
  
  mutate(receipts = Quantity*USPrice, full_name = paste(first_name,last_name)) %>% 
  select(full_name,receipts) %>%
  group_by(full_name) %>% 
  summarize(total_receipts = sum(receipts)) %>%
  arrange(desc(total_receipts) ) %>%
  filter(total_receipts >= unique(total_receipts)[5]) %>%
  kable()
```

The table above shows the five customers have spent the most money so far. To find which customers have spent the most money, we first calculate the total money each customer spent on lego and arrange them into a list in descending order by how much money they spend. The top 5 of the list will be the five customers who spent the most money so far.

<br/>

4. Which lego theme has made the most money for lego?

```{r}
lego_sales %>% 
  mutate (receipts = Quantity*USPrice) %>% 
  select(Theme,receipts) %>%
  group_by(Theme) %>%
  summarize(total = sum(receipts)) %>%
  filter(total == max(total)) %>%
  kable()

```

Star Wars made the most money for lego. We calculate the total money moade by each theme and rank them by the money they made.

<br/>

5. Do men or women buy more lego sets (per person) on average?

```{r}
lego_sales %>%
  select(gender,Quantity) %>%
  group_by(gender) %>% 
  summarize(avg_sets = mean(Quantity)) %>%
  kable()

```

Men buy more lego sets per person on average. We calculate the average money spent by gender and compare the two.

<br/>

6. What are the five most popular hobbies of lego purchasers?

```{r}
t1 = lego_sales %>% 
  select(hobbies) %>% 
  unlist() %>% 
  sort()

t2 = sapply(unique(t1), function(x){sum(t1 == x)}) %>% 
  sort(.,decreasing = TRUE)

hobbies = t2[t2 >= t2[5]] %>% 
  as.data.frame() %>%
  kable(.,col.names = c(""))

hobbies
```

We unlist the variables in column hobbies and count the number of times each hobby appears. From the result above we can see the five most popular hobbies of lego purchasers.

<br/>

7. How many total pieces have been purchased from lego by these customers?

```{r}

lego_sales %>% 
  mutate(t_pieces = Quantity*Pieces) %>% 
  select(t_pieces) %>% 
  summarize(total = sum(na.omit(t_pieces))) %>%
  kable()

```

To calculate the total pieces, we first caculate the total pieces for each customer, then calculate the sum of total pieces for each customer, omitting observations that have missing values.

<br/>

8. Which area code has spent the most money on legos?

```{r}
lego_sales %>% 
  mutate(area_code = substr(phone_number,1,3), receipts = USPrice*Quantity) %>% 
  select(area_code,receipts) %>%
  group_by(area_code) %>%
  summarize(total_area = sum(receipts)) %>% 
  filter(!is.na(area_code)) %>% 
  filter(total_area == max(total_area)) %>%
  kable()

```

We first create a list of area code by choosing the first three numbers of the phone number. We then calculate the total money spent by each area code, and find out the area code that has spent the most money on legos.


