Homework 2 - [Your team name here]
========================================================

### Task 0 - Load the data

```{r message = FALSE}
library(dplyr)
library(purrr)
library(tibble)
library(repurrrsive)
library(stringr)

load("lego_sales.RData")
```


### Task 1 - Tidying the data

<!-- Covert the `sales` object into a tidy data frame. Be sure to include a write up of your methods. -->

```{r}
d=data_frame(
first_name=map_chr(sales,"first_name"),
last_name=map_chr(sales,"last_name"),
gender=map_chr(sales,"gender"),
age=map_dbl(sales,"age")
)

num_purchases=rep(0,250)
for(i in 1:250)
{
  temp=unlist(sales[i])
  nam=temp[names(temp)=="purchases.Number"]
  num_purchases[i]=length(nam)
}

dd=as.matrix(d)
ii=0;
final<-matrix(nrow=620,ncol=4)
for (j in 1:250)
{
  for(e in 1:num_purchases[j])
  {
    final[ii+e,]=dd[j,]
  }
  ii=ii+num_purchases[j]
}
```


<br/>

## Task 2 - Processing the data


1. What was the most common first name of purchasers? Last name?

```{r}
```

2. What are the five most popular lego sets based on these data?

```{r}
```

3. Which five customers have spent the most money so far and how much have they spent?

```{r}
```

4. Which lego theme has made the most money for lego?

```{r}
```

5. Do men or women buy more lego sets (per person) on average?

```{r}
```

6. What are the five most popular hobbies of lego purchasers?

```{r}
```

7. How many total pieces have been purchased from lego by these customers?

```{r}
```

8. Which area code has spent the most money on legos?

```{r}
```
