Homework 2 - [Your team name here]
========================================================

### Task 0 - Load the data

```{r message = FALSE}
library(dplyr)
library(purrr)
library(tibble)
library(repurrrsive)
library(stringr)

load("lego_sales.RData")
```


### Task 1 - Tidying the data

<!-- Covert the `sales` object into a tidy data frame. Be sure to include a write up of your methods. -->

```{r}
list_cols = map(sales, ~ map_int(., length) )  %>% 
     map(~ which(. > 1)) %>% 
     unlist() %>% 
     names() %>% 
     unique()

d=map_df(
     sales, 
     function(row)
     {
         map_at(row, list_cols, list)
     }
 )

d$purchases <-NULL

num_purchases=rep(0,250)
for(i in 1:250)
{
  temp=unlist(sales[i])
  nam=temp[names(temp)=="purchases.Number"]
  num_purchases[i]=length(nam)
}

final = d %>%slice(rep(1:n(), num_purchases))

half2<-matrix(data=NA, nrow=sum(num_purchases),ncol=10)
iii=0
for (w in 1:250)
{
  temp=unlist(sales[w])
  for (ww in 1:num_purchases[w])
  {
    name1=temp[names(temp)=="purchases.SetID"][ww]
    name2=temp[names(temp)=="purchases.Number"][ww]
    name3=temp[names(temp)=="purchases.Theme"][ww]
    name4=temp[names(temp)=="purchases.Subtheme"][ww]
    name5=temp[names(temp)=="purchases.Year"][ww]
    name6=temp[names(temp)=="purchases.Name"][ww]
    name7=temp[names(temp)=="purchases.Pieces"][ww]
    name8=temp[names(temp)=="purchases.USPrice"][ww]
    name9=temp[names(temp)=="purchases.ImageURL"][ww]
    name10=temp[names(temp)=="purchases.Quantity"][ww]
    tempp=cbind(name1,name2,name3,name4,name5,name6,name7,name8,name9,name10)
    half2[iii+ww,]=tempp
  }
  iii=iii+num_purchases[w]
}
colnames(half2)=cbind("purchases.SetID","number","theme","subtheme","year","name","pieces","usprice","imageurl","quantity")
kkk=cbind(final,half2)
lego_sales=as.data.frame(kkk)
  
```


<br/>

## Task 2 - Processing the data


1. What was the most common first name of purchasers? Last name?

```{r}
```

2. What are the five most popular lego sets based on these data?

```{r}
sort(table(lego_sales$purchases.SetID),decreasing = T)[1:5]
#Yunxuan
```

3. Which five customers have spent the most money so far and how much have they spent?

```{r}
```

4. Which lego theme has made the most money for lego?

```{r}
```

5. Do men or women buy more lego sets (per person) on average?

```{r}
```

6. What are the five most popular hobbies of lego purchasers?

```{r}
```

7. How many total pieces have been purchased from lego by these customers?

```{r}
total_pieces<-sum(na.omit(as.numeric(as.character(lego_sales$pieces))))

ttp<-as.character(lego_sales$pieces)%>%
  as.numeric()%>%
  na.omit()%>%
  sum()
#by yunxuan
```

8. Which area code has spent the most money on legos?

```{r}
```
